GBIF invasive species

### 2021-04-06 analysis/invasive_data.Rmd
get invasive data

Figure out which country each study is located in 
```{r}
pins::board_register_github(name = "github", repo = "karinorman/biodivTS_data", branch = "master")
options(geonamesUsername="getafreeusernamefromgeonames.org")
options(gbif_u)

@@

>>>>

Figure out which country each study is located in 
```{r}
pins::board_register_github(name = "github", repo = "karinorman/biodivTS_data", branch = "master")
options(geonamesUsername="karinorman")

@@

Read in Invasive Data
```{r}
invasive_files <- list.dirs(here::here("data", "invasive"))

taxon <- read_tsv(paste0(invasive_files[2], "/", "taxon.txt"))
profile <- read_tsv(paste0(invasive_files[2], "/", "speciesprofile.txt"))
dist <- read_tsv(paste0(invasive_files[2], "/", "distribution.txt")) %>%
  select(id, countryCode)

data <- left_join(taxon, profile) %>% left_join(dist)
